Longitudinal Data Analysis with the ABCD Study

### 2024-03-21 index.qmd
update toolbar
toolbar update

---
#title: "Longitudinal Data Analysis with the ABCD Study"
format:
  html:
    css: styles.css

@@

::: {.callout-important}
**Note**: This project is currently in beta. [Examples](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) are under development and may not be ready for direct application. Your feedback and contributions are invaluable to us—join us in enhancing these resources. For more details on contributing, visit our [GitHub repository](https://github.com/OpenDevSci/LongDev-ABCD) and our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md).
:::

>>>>

format:
  html:
    css: styles.css

@@

::: {.callout-important}
**Note**: This project is currently in beta. [Examples](https://opendevsci.github.io/LongDev-ABCD/examples/examples.html) are under development and may not be ready for direct application. Your feedback and contributions are invaluable to us—join us in enhancing these resources. For more details on contributing, visit our [GitHub Repository](https://github.com/OpenDevSci/LongDev-ABCD) and our [Contribution Guide](https://github.com/OpenDevSci/LongDev-ABCD/blob/main/docs/Contributing.md).
:::
